### 2020-03-26 Common/chapters/transfer_learning.tex
Johan and Julien: minor
Julien and Johan: minor

\begin{enumerate}
	\item The model saved at the end of the previous training is loaded. Its last layers (the decision maker) are completely reset, i.e. the weights are reset to another initialization, as if no training occured for these layers. Afterwards, the first layers (the feature extractor) are frozen and the model is trained. Since the first layers have been frozen, their weights remain the same. Only the weights of the last layers change during this training. This part of the transfer learning allows the model to make use of the previously learned features while adapting to the new body part by training the decision maker. 
	\item Once the training with frozen layers is over, the best model is loaded, the frozen layers are unfrozen, and a normal training is performed on the same dataset. Thanks to this, the model adapts the previously learned features and tries to learn new features which could be useful for the classification of the target dataset. 
\end{enumerate}
\item Fifth, the previous step is also applied to the target dataset. The only difference lies in the frozen part. Instead of dropping the old last layers and initialize their weights randomly, the decision maker of the best model found during the training on the first dataset is attached to the model. These final two trainings aim at keeping the interesting features from the other datasets while learning specializing the model in the target dataset again. Hopefully, the new weight initialization resulting from the transfer learning will allow to reach better metric values than before the transfer learning.

>>>>

\begin{enumerate}
	\item The model saved at the end of the previous training is loaded. Its last layers (the decision maker) are completely reset, i.e. the weights are reset to another initialization, as if no training occured for these layers. Afterwards, the first layers (the feature extractor) are frozen and the model is trained. Since the first layers have been frozen, their weights remain the same. Only the weights of the last layers change during this training. This part of the transfer learning allows the model to make use of the previously learned features while adapting to the new body part by training the decision maker. 
	\item Once the training with frozen layers is over, the best model is loaded, the frozen layers are unfrozen, and a normal training is performed on the same dataset. Thanks to this, the model adapts the previously learned features and tries to learn new features which could be useful for the classification of the target dataset. 
\end{enumerate}
\item Fifth, the previous step is also applied to the target dataset. The only difference lies in the frozen part. Instead of dropping the old last layers and initializing their weights randomly, the decision maker of the best model found during the training on the first dataset is attached to the model. These final two trainings aim at keeping the interesting features from the other datasets while learning specializing the model in the target dataset again. Hopefully, the new weight initialization resulting from the transfer learning will allow to reach better metric values than before the transfer learning.
